Analysis of Hate Crimes in Toronto From 2018 to 2023

### 2024-09-27 output/paper.qmd
final

---
title: "Rising Hate Crimes in Toronto: Increased Targeting of Jewish People and Public Incidents"
author: "Boxuan Yi"
format: pdf
abstract: "Hate crime data provide valuable insights into underlying biases and social dynamics. This paper analyzes hate crime reports from Open Data Toronto between 2018 and 2023, focusing on the distribution of crimes by target group and location. The analysis reveals that Jewish people are the most frequently targeted group, followed by Black individuals, and the number of incidents continues to rise. Additionally, nearly half of hate crimes occur in public spaces/transportation, highlighting the growing threat to safety in everyday environments."
date: "26 September 2024"
date-format: "D MMMM YYYY"
number-sections: true
thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/hate_crimes_in_toronto"
bibliography: references.bib
toc: true
---
\newpage
# Introduction {#sec-introduction}
```{r}
#| include: false
library(dplyr)
library(tidyverse)
library(here)
library(janitor)
library(knitr)
library(ggplot2)
```

@@

This paper seeks to fill this gap by analyzing hate crime data from Open Data Toronto, spanning 2018 to 2023. The goal is to identify which biased groups, including those based on race, religion, and disability, are most frequently targeted, and to examine the locations and types of settings where these crimes occur. The results show that a significant proportion of hate crimes were directed at Black individuals and Jewish people, accounting for approximately 16% and 31% of incidents, respectively. About half of the crimes occurred in public spaces or on transportation, and roughly half were property crimes, with increasing trends observed in educational and commercial/business settings. These trends not only highlight the vulnerability of these groups but also point to an increasing threat in everyday public environments, emphasizing the need for stronger interventions.

>>>>

---
title: "Analysis of Hate Crimes in Toronto From 2018 to 2023"
subtitle: "Increasing Targeting of Jewish People and Rising Public Incidents"
author: "Boxuan Yi"
format: pdf
abstract: "Hate crime data provide valuable insights into underlying biases and social dynamics. This paper analyzes hate crime reports from Open Data Toronto between 2018 and 2023, focusing on the distribution of crimes by target group and location. The analysis reveals that Jewish people are the most frequently targeted group, followed by Black individuals, and the number of incidents continues to rise. Additionally, nearly half of hate crimes occur in public spaces/transportation, highlighting the growing threat to safety in everyday environments."
date: "26 September 2024"
date-format: "D MMMM YYYY"
number-sections: true
thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/hate_crimes_in_toronto"
bibliography: references.bib
toc: true
---
\newpage
# Introduction {#sec-introduction}
```{r}
#| include: false
library(dplyr)
library(tidyverse)
library(here)
library(janitor)
library(knitr)
library(ggplot2)
```

@@

This paper seeks to fill this gap by analyzing hate crime data from Open Data Toronto, spanning 2018 to 2023 [@hatecrime]. The goal is to identify which biased groups, including those based on race, religion, and disability, are most frequently targeted, and to examine the locations and types of settings where these crimes occur. The results show that a significant proportion of hate crimes were directed at Black individuals and Jewish people, accounting for approximately 16% and 31% of incidents, respectively. About half of the crimes occurred in public spaces or on transportation, and roughly half were property crimes, with increasing trends observed in educational and commercial/business settings. These trends not only highlight the vulnerability of these groups but also point to an increasing threat in everyday public environments, emphasizing the need for stronger interventions.
